---
title: "Lucius Groot Homework Week 7"
output: html_document
date: "2024-02-14"
---
```{r}
```
I start this with loading the library: tidyverse and spotifyr
```{r}
library(tidyverse)
library(spotifyr)
```
I need the listss, which are 2 at this moment. 
The first lists consist of music that I used to listen between the age 2 till 12. All of these are stored at home in CD's or are DVD's showtunes intro.
The second lists is my weekly discovery, which is based on my current taste in music (mostly musical theatre songs and jazz/fusion/pop/rock/country etc, too much to sum up).
I am using short cuts for both the lists, which I also will make in the following chunck

```{r}
      #Uploading "Music of Lucius' Childhood" to RStudios via URL; this lists contains the songs I have at home in CD form and showtunes          from TV shows.
MoLC <- get_playlist_audio_features("", "7E5lKSGKAhGwQZaftQViGz") 
        
      #uploading "Discover Weekly on 14 February 2024 of Lucius' Spotify" via URL. 
dw0 <- get_playlist_audio_features("", "37i9dQZEVXcIgiZXlwTluc") 

#shortcut for "Music of Lucius' Childhood" and "Discover Weekly on 14 February 2024 of Lucius' Spotify"
lists <-
  bind_rows(
    MoLC |> mutate(category = "Music of Lucius' Childhood"),
    dw0 |> mutate(category = "discovery weekly week 0 of Lucius")
  )
```
The summary I let Rstudio made of both the lists:
I am interested how fast discover weekly will be adapted to the results of my childhood music
```{r}
#summary of "Discover Weekly on 14 February 2024 of Lucius' Spotify"
dw0 |>
  summarise(
    mean_speechiness = mean(speechiness),
    mean_acousticness = mean(acousticness),
    mean_liveness = mean(liveness),
    sd_speechiness = sd(speechiness),
    sd_acousticness = sd(acousticness),
    sd_liveness = sd(liveness),
    median_speechiness = median(speechiness),
    median_acousticness = median(acousticness),
    median_liveness = median(liveness),
    mad_speechiness = mad(speechiness),
    mad_acousticness = mad(acousticness),
    mad_liveness = mad(liveness)
  ) 

#summary of  "Music of Lucius' Childhood"
MoLC |>
  summarise(
    mean_speechiness = mean(speechiness),
    mean_acousticness = mean(acousticness),
    mean_liveness = mean(liveness),
    sd_speechiness = sd(speechiness),
    sd_acousticness = sd(acousticness),
    sd_liveness = sd(liveness),
    median_speechiness = median(speechiness),
    median_acousticness = median(acousticness),
    median_liveness = median(liveness),
    mad_speechiness = mad(speechiness),
    mad_acousticness = mad(acousticness),
    mad_liveness = mad(liveness)
  )

#I do not know how I can facet this one unfortunately
```
I want to know of both the lists:
Valence versus energy + the mode
```{r}
  #the plots combined
ggplot(lists, aes(x = valence, y = energy, color = mode )) +
  geom_point(size = 1) +
  geom_segment(aes(xend = valence, yend = energy), size = 0.1) + 
  facet_wrap(~category) + 
   ggtitle("plot of my listss, valence versus energy combined with mode")

  #the plots individual: dw0
ggplot(dw0, aes(valence, energy)) +
  geom_point(aes(colour= mode)) +
  scale_y_log10() +
   ggtitle("plot of discovery weekly week 0 of Lucius, valence versus energy combined with mode")

  #the plots individual: MoLC
ggplot(JM, aes(x = valence, y = energy, color = mode)) +
  geom_point() +
  ggtitle("plot of Music of Lucius Childhood, valence versus energy combined with mode")

```
I want to know of both the lists:
Valence versus energy + the mode, but with a smooth curve, so I can see an average

```{r}
  #the plots combined
lists |> ggplot(aes(x = valence, y = energy)) + geom_point() + geom_smooth() + 
  facet_wrap(~category) + 
  ggtitle("Smoothcurve of my listss, valence versus energy combined with mode")
  
  #the plots individual: dw0 
dw0 |> ggplot(aes(x = valence, y = energy)) + geom_point() + geom_smooth() +
    ggtitle("Smoothcurve of dw0, valence versus energy combined with mode")

  #the plots individual: MoLC
MoLC |> ggplot(aes(x = valence, y = energy)) + geom_point() + geom_smooth() +
    ggtitle("Smoothcurve of Music of Lucius Childhood, valence versus energy combined with mode")

```
``` 
I took some inspiration of the homework for my longest code ever
```
```{r}
#making 2 plots in one plot, i want to compare my weekly discovery with computational musicology playlist
lists |>                    #I started with the 2 playlists
  mutate(
    mode = ifelse(mode == 0, "Minor", "Major")
  ) |>
  ggplot(                     #This is the code I used for making the plot with ggplot2, i took inspiration from the assignment during the class
    aes(
      x = valence,
      y = energy,
      size = loudness,
      colour = mode
    )
  ) +
  geom_point() +              #first I tried to make a scatterplot
  geom_rug(linewidth = 0.02) + #deciding that the border is 0.02
  geom_text(                  #valence versus energy labels
    aes(
      x = valence,
      y = energy,
      label = label
    ),
    data = 
      tibble(
        label = c("", "  "),
        category = c("Music of Lucius' Childhood"),
        valence = c(0.104, 0.0339),
        energy = c(0.992, 0.00166)
      ),
    colour = "black",         #colour of the plot is black
    size = 4,                 #i want the size of the plot to be 4
    hjust = "left",           #i was making left side
    vjust = "center",         #i was making right side
    nudge_x = 0.02            #i wanted to place the label slightly to the right
  ) +
  facet_wrap(~ category) +    #i decided that i wanted to use both my playlist in two plots in one, again
  scale_x_continuous(         #i decided to fine-tune the x axis
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),   #i used grid-lines for quadrants only.
    minor_breaks = NULL       #i wanted to remove 'minor' grid-lines.
  ) +
  scale_y_continuous(         #i fine-tuned the y axis in the same way.
    limits = c(0, 1),
    breaks = c(0, 0.50, 1),
    minor_breaks = NULL
  ) +
  scale_colour_brewer(        #the color brewer i used for making a was palette
    type = "qual",            #i have a qualitative set
    palette = "Paired"        #i named the palette to 'Paired'
  ) +
  scale_size_continuous(      #i decided to also fine-tune the sizes of each point
    trans = "exp",            #i used an exp transformation to emphasise loud
    guide = "none"            #i remove the legend for size, did not need it
  ) +
  theme_light() +             #making the theme light
  labs(
    x = "Valence",
    y = "Energy",
    colour = "Mode"
  )

```
The histogram I made about both the lists:
```{r}
#histogram of discovery weekly week 0 and Lucius & Music of Lucius' Childhood together in one plot
lists |>
  ggplot(aes(x = energy)) +
  geom_histogram(binwidth = 0.1) +
  facet_wrap(~category) + ggtitle("discovery weekly week 0 and Lucius & Music of Lucius' Childhood")
```
What do I want to know? 
Will all the next Discovery weekly lists become more as Music of Lucius's Childhood? 
Which kind of songs will spotify recommend?
Which codes can I use the best
Will spotify recommend disney or more music with Dutch as language instead of English or music animatie compagnie (work i used to listen during a job at a camping in the holidays)
